\documentclass[11pt]{article}

% Packages for math, formatting, and graphics
\usepackage[utf8]{inputenc}
\usepackage{amsmath, amssymb, amsthm}
\usepackage[margin=1in]{geometry}
\usepackage{graphicx}
\usepackage[most]{tcolorbox} % Added [most] to enable breakable boxes
\usepackage{hyperref}
\usepackage{enumitem}

% Setup custom colored boxes to match the HTML styling
% Added "breakable" so long derivation boxes flow perfectly across pages
\newtcolorbox{defbox}[1]{colback=blue!5, colframe=blue!75!black, fonttitle=\bfseries, title={#1}, arc=4pt, boxrule=1pt, left=10pt, right=10pt, top=10pt, bottom=10pt, breakable}
\newtcolorbox{warnbox}[1]{colback=yellow!10, colframe=orange!90!black, fonttitle=\bfseries, title={#1}, arc=4pt, boxrule=1pt, left=10pt, right=10pt, top=10pt, bottom=10pt, breakable}
\newtcolorbox{stepbox}[1]{colback=white, colframe=gray!40, fonttitle=\bfseries, coltitle=black, title={#1}, arc=4pt, boxrule=1pt, left=10pt, right=10pt, breakable}

\title{\textbf{Quasi-Exact Differential Forms \& Hodge Decomposition}}
\author{Stefano Nicotri}
\date{}

\begin{document}

\maketitle

\begin{abstract}
\noindent In classical vector calculus and differential geometry, fields are often categorized in a binary way: they are either perfectly conservative (exact) or they are path-dependent (non-exact). However, in real-world physics, "non-exactness" is rarely an all-or-nothing property. A flow might be overwhelmingly conservative, driven entirely by a potential gradient, but contaminated by a tiny, localized vortex. 

This document explores the concept of \textbf{quasi-exactness}---the mathematical framework used to definitively measure exactly \textit{how} conservative a path-dependent field is. By utilizing the \textbf{Hodge Decomposition Theorem}, we can mathematically slice any messy, non-exact differential form into perfectly orthogonal "exact" (gradient) and "co-exact" (swirling) components. By comparing the $L^2$ norms (energies) of these separated layers, we can assign a strict, quantitative percentage to the field's exactness.
\end{abstract}

\vspace{1em}

\section{Formal Definitions and Framework}
Before decomposing a form, we rigorously define the space it lives in and the operators acting upon it. Let $M$ be an $n$-dimensional oriented Riemannian manifold.

\begin{defbox}{The Space of Differential $k$-forms ($\Omega^k(M)$)}
A \textbf{differential $k$-form} is a completely antisymmetric covariant $k$-tensor field. Geometrically, at every point $p$ on the manifold $M$, it assigns an alternating, multilinear map that takes $k$ tangent vectors as input and yields a real number (a scalar):
\[ \omega_p : \underbrace{T_p M \times \dots \times T_p M}_{k \text{ times}} \to \mathbb{R} \]
The collection of all such smooth $k$-forms over the entire manifold forms an infinite-dimensional vector space denoted as $\mathbf{\Omega^k(M)}$. To build intuition:
\begin{itemize}[noitemsep]
    \item \textbf{$\Omega^0(M)$ (0-forms):} Smooth scalar functions, like potential energy $f(x,y)$.
    \item \textbf{$\Omega^1(M)$ (1-forms):} Covector fields, which naturally integrate over lines/curves (e.g., work, circulation).
    \item \textbf{$\Omega^2(M)$ (2-forms):} Objects that naturally integrate over surfaces (e.g., magnetic flux).
    \item \textbf{$\Omega^n(M)$ ($n$-forms):} Top-forms, representing the fundamental volume elements for the space.
\end{itemize}
\end{defbox}

\begin{defbox}{The Exterior Derivative ($d$)}
The exterior derivative is a coordinate-free differential operator $d: \Omega^k(M) \to \Omega^{k+1}(M)$ that generalizes the concepts of the gradient, curl, and divergence from vector calculus. It maps a $k$-form to a $(k+1)$-form and satisfies three crucial properties:
\begin{enumerate}[noitemsep]
    \item \textbf{Gradient Action:} For a 0-form (scalar function) $f$, $df$ is its standard differential.
    \item \textbf{Graded Leibniz Rule:} For a $k$-form $\alpha$ and any form $\beta$, $d(\alpha \wedge \beta) = d\alpha \wedge \beta + (-1)^k \alpha \wedge d\beta$.
    \item \textbf{Nilpotence:} $d^2 = d \circ d = 0$. Geometrically, this expresses the profound topological principle that "the boundary of a boundary is zero."
\end{enumerate}
\end{defbox}

\begin{defbox}{The Hodge Star Operator ($\star$)}
The Hodge star is a linear isomorphism $\star: \Omega^k(M) \to \Omega^{n-k}(M)$ that depends entirely on the manifold's metric tensor $g$ and its orientation. It formally maps a $k$-dimensional form to its orthogonal $(n-k)$-dimensional "complement" (its dual).

\textbf{General Definition:} On an $n$-dimensional oriented Riemannian manifold with a volume form $dV$, the Hodge star is uniquely defined by the relation:
\[ \alpha \wedge \star\beta = \langle \alpha, \beta \rangle_g \, dV \]
where $\alpha$ and $\beta$ are any two $k$-forms, and $\langle \alpha, \beta \rangle_g$ is the local inner product induced by the metric.

\textbf{Specialization to $\mathbb{R}^2$:} In 2D Euclidean space ($n=2$) with volume form $dV = dx \wedge dy$, the Hodge star geometrically acts as a 90-degree rotation on 1-forms:
\[ \star dx = dy, \quad \star dy = -dx \]
\[ \star 1 = dx \wedge dy, \quad \star(dx \wedge dy) = 1 \]

\textbf{Specialization to $\mathbb{R}^3$:} In 3D Euclidean space ($n=3$) with volume form $dV = dx \wedge dy \wedge dz$, the Hodge star establishes the duality between 1-forms and 2-forms, mimicking the cross product:
\[ \star dx = dy \wedge dz, \quad \star dy = dz \wedge dx, \quad \star dz = dx \wedge dy \]
\[ \star(dy \wedge dz) = dx, \quad \star(dz \wedge dx) = dy, \quad \star(dx \wedge dy) = dz \]

\textbf{Specialization to $\mathbb{R}^4$:} In 4D Euclidean space ($n=4$), the Hodge star maps 2-forms directly to other 2-forms, forming the foundation of \textit{self-dual} fields in gauge theory:
\[ \star(dx_1 \wedge dx_2) = dx_3 \wedge dx_4 \]
\[ \star(dx_1 \wedge dx_3) = -dx_2 \wedge dx_4 \]
\[ \star(dx_1 \wedge dx_4) = dx_2 \wedge dx_3 \]
\end{defbox}

\begin{defbox}{The $L^2$ Inner Product and Codifferential ($\delta$)}
\textbf{Inner Product:} For two $k$-forms $\alpha, \beta \in \Omega^k(M)$, the global $L^2$ inner product is defined as:
\[ \langle \alpha, \beta \rangle_{L^2} = \int_M \alpha \wedge \star\beta \]
This induces a norm $\|\omega\|^2 = \langle \omega, \omega \rangle_{L^2}$, representing the total "energy" of the field.

\textbf{Codifferential:} The formal adjoint of $d$ is the codifferential $\delta: \Omega^k \to \Omega^{k-1}$, which acts as a generalized divergence:
\[ \delta = (-1)^{n(k-1)+1} \star d \star \]
Because $d^2 = 0$, it immediately follows that $\delta^2 = 0$.
\end{defbox}

\section{The Hodge Decomposition Theorem}
The Hodge Decomposition states that the space of differential $k$-forms on a closed Riemannian manifold splits into three mutually orthogonal subspaces:
\[ \Omega^k(M) = d\Omega^{k-1}(M) \oplus \delta\Omega^{k+1}(M) \oplus \mathcal{H}^k(M) \]

Any $k$-form $\omega$ can be uniquely written as $\omega = d\alpha + \delta\beta + \gamma$, where:
\begin{itemize}[noitemsep]
    \item \textbf{$d\alpha$ (Exact Component):} Path-independent. Analogous to a gradient flow.
    \item \textbf{$\delta\beta$ (Co-Exact Component):} Divergence-free. Analogous to circulating flows/swirls.
    \item \textbf{$\gamma$ (Harmonic Component):} Forms satisfying $\Delta_{dR} \gamma = (d\delta + \delta d)\gamma = 0$. These depend strictly on the manifold's topology (holes).
\end{itemize}

\section{Solving the Differential Equations (2D Disk)}
Let's decompose a specific non-exact 1-form in Cartesian coordinates $(x,y)$ over the unit disk $D$ where $x^2 + y^2 \le 1$:
\[ \omega = x^2y \, dx + xy^2 \, dy \]
Because $\mathbb{R}^2$ has no holes, the harmonic component $\gamma = 0$. Our decomposition is $\omega = df + \delta\beta$, where $f(x,y)$ is a scalar 0-form and $\beta = g(x,y) dx \wedge dy$ is a 2-form. By applying the operators $d$ and $\delta$, we decouple this into two standard Poisson equations:
\[ \nabla^2 f = -\delta\omega = 4xy \]
\[ \nabla^2 g = -\star d\omega = x^2 - y^2 \]

\subsection*{Mathematical Appendix 1: Proof of the Decoupling}
The decoupling relies on the nilpotence of the operators ($d^2 = 0$ and $\delta^2 = 0$). Starting with $\omega = df + \delta\beta$:

\textbf{Part 1: Isolating the Exact Potential ($f$)}
\begin{enumerate}[noitemsep]
    \item Apply $\delta$ to both sides: $\delta\omega = \delta(df) + \delta(\delta\beta)$
    \item Apply Nilpotence ($\delta^2 = 0$): $\delta\omega = \delta d f + 0$
    \item Convert to standard Laplacian: For a scalar $f$, $\delta d f = -\nabla^2 f$. Thus, $\nabla^2 f = -\delta\omega$.
\end{enumerate}

\textbf{Part 2: Isolating the Co-Exact Potential ($g$)}
\begin{enumerate}[noitemsep]
    \item Apply $d$ to both sides: $d\omega = d(df) + d(\delta\beta)$
    \item Apply Nilpotence ($d^2 = 0$): $d\omega = 0 + d\delta\beta$
    \item Expand $\delta\beta$ in 2D: $\delta\beta = -\star d \star (g \, dx \wedge dy) = g_y dx - g_x dy$
    \item Apply $d$ and convert: $d(\delta\beta) = -(\nabla^2 g) dx \wedge dy$. Applying the Hodge star yields $\nabla^2 g = -\star d\omega$.
\end{enumerate}

\begin{warnbox}{Note on Notation: The Geometer's vs. Physicist's Laplacian}
The general operator acting on forms is the \textbf{Laplace-de Rham operator}, $\Delta_{dR} = \delta d + d\delta$.
For a 0-form $f$, $\delta f = 0$, so $\Delta_{dR} f = \delta d f$.
Geometers define $\Delta_{dR}$ to be \textit{positive-definite}. However, the standard physics Laplacian $\nabla^2 f = \nabla \cdot \nabla f$ is \textit{negative-definite}. Therefore, we must write $\Delta_{dR} f = \delta d f = -\nabla^2 f$.
\end{warnbox}

\subsection*{Mathematical Appendix 2: Deriving the Boundary Conditions}
To understand why the boundary conditions must be set up this way, we translate our differential forms into standard 2D vector fields.

\begin{defbox}{Clarifying Vector Notation}
In the math below, you will see vectors written with angle brackets, like $\langle \omega_x, \omega_y \rangle$. It is extremely important to note that \textbf{this is not an inner product (scalar product)}. In vector calculus, angle brackets are frequently used as \textit{component notation} to define a vector's horizontal and vertical parts, distinguishing it from a coordinate point $(x,y)$.
\end{defbox}

\begin{itemize}[noitemsep]
    \item Original 1-form vector field: $\vec{V} = \langle \omega_x, \omega_y \rangle = \omega_x \hat{i} + \omega_y \hat{j}$
    \item Exact part ($df$) as a gradient field: $\vec{E} = \nabla f = \langle f_x, f_y \rangle = f_x \hat{i} + f_y \hat{j}$
    \item Co-exact part ($\delta\beta$) as a curl field: $\vec{C} = \nabla \times (g \hat{k}) = \langle g_y, -g_x \rangle = g_y \hat{i} - g_x \hat{j}$
\end{itemize}

Our decomposition is $\vec{V} = \vec{E} + \vec{C}$. For the total energy to split perfectly, the cross-energy overlap between the two separated fields must be exactly zero over the entire disk $D$:
\[ \iint_D (\vec{E} \cdot \vec{C}) \, dA = \iint_D (\nabla f \cdot \vec{C}) \, dA = 0 \]

\subsubsection*{1. Applying the Divergence Theorem}
Using the vector identity $\nabla \cdot (f\vec{C}) = \nabla f \cdot \vec{C} + f(\nabla \cdot \vec{C})$ and noting that the divergence of a curl is zero ($\nabla \cdot \vec{C} = 0$), we rewrite the integral:
\[ \iint_D \nabla \cdot (f\vec{C}) \, dA \]
By the Divergence Theorem, this 2D area integral becomes a 1D line integral around the boundary curve $\partial D$:
\[ \iint_D \nabla \cdot (f\vec{C}) \, dA = \oint_{\partial D} f (\vec{C} \cdot \hat{n}) \, ds \]

For orthogonality, this boundary integral \textbf{must be zero} for any arbitrary scalar potential $f$. Therefore, we are forced to set:
\[ \vec{C} \cdot \hat{n} = 0 \text{ on } \partial D \]

\subsubsection*{2. The Geometry of the Boundary ($\hat{n}$ and $\hat{t}$)}
To evaluate the fields at the boundary of the unit circle ($x^2 + y^2 = 1$), we need its outward unit normal vector $\hat{n}$ and its counter-clockwise unit tangent vector $\hat{t}$.

\begin{itemize}
    \item \textbf{The Outward Normal ($\hat{n}$):} There are two ways to mathematically confirm this:
    \begin{itemize}
        \item \textit{The Geometric Approach:} The position vector pointing from the origin to any point $(x,y)$ on the unit circle is $\vec{r} = x\hat{i} + y\hat{j}$. Since a radius is always perpendicular to the circle's tangent, and its length is $\sqrt{x^2+y^2} = 1$, this position vector is exactly our outward unit normal: $\hat{n} = x\hat{i} + y\hat{j}$.
        \item \textit{The Calculus Approach (Gradient):} Define the 2D plane with the function $F(x,y) = x^2 + y^2$. The unit circle is simply the level curve $F(x,y) = 1$. The gradient $\nabla F$ always points perpendicular to level curves, giving us $\nabla F = 2x\hat{i} + 2y\hat{j}$. To make it a unit vector, we divide by its magnitude on the circle ($\|\nabla F\| = \sqrt{(2x)^2+(2y)^2} = 2\sqrt{x^2+y^2} = 2(1) = 2$). Therefore, $\hat{n} = \frac{\nabla F}{\|\nabla F\|} = \frac{2x\hat{i} + 2y\hat{j}}{2} = x\hat{i} + y\hat{j}$.
    \end{itemize}
    \item \textbf{The Tangent Vector ($\hat{t}$):} A tangent vector must be perfectly orthogonal to the normal, meaning their dot product is zero ($\hat{n} \cdot \hat{t} = 0$). By swapping the $x$ and $y$ components and negating one, we satisfy this: $x(-y) + y(x) = 0$. We choose $\hat{t} = -y\hat{i} + x\hat{j}$ (rather than $y\hat{i} - x\hat{j}$) because evaluating it at $(1,0)$ gives $0\hat{i} + 1\hat{j}$, which points UP, matching the standard counter-clockwise (positive) orientation required by Green's Theorem.
\end{itemize}

\subsubsection*{3. The Dirichlet Condition for $g$}
Using the boundary vectors derived above, let's calculate $\vec{C} \cdot \hat{n}$:
\[ \vec{C} \cdot \hat{n} = \langle g_y, -g_x \rangle \cdot \langle x, y \rangle = x g_y - y g_x \]
Notice that the directional derivative of $g$ along the boundary tangent $\hat{t}$ is identical:
\[ \frac{\partial g}{\partial t} = \nabla g \cdot \hat{t} = \langle g_x, g_y \rangle \cdot \langle -y, x \rangle = -y g_x + x g_y \]
Therefore, $\vec{C} \cdot \hat{n} = \frac{\partial g}{\partial t} = 0$. If the tangential derivative of $g$ is zero, $g$ must be constant on the boundary. We choose $g = 0$, giving us our \textbf{Dirichlet condition}.

\subsubsection*{4. The Neumann Condition for $f$}
Taking the dot product of our original decomposition $\vec{V} = \vec{E} + \vec{C}$ with the normal vector $\hat{n}$ gives:
\[ \vec{V} \cdot \hat{n} = \vec{E} \cdot \hat{n} + \vec{C} \cdot \hat{n} \]
Since we enforced $\vec{C} \cdot \hat{n} = 0$, that term vanishes. Substituting $\vec{E} = \nabla f$ gives:
\[ \vec{V} \cdot \hat{n} = \nabla f \cdot \hat{n} = \frac{\partial f}{\partial n} \text{ on } \partial D \]
The exact part $f$ absorbs 100\% of the normal boundary flux of the original field $\vec{V}$, giving us our \textbf{Neumann condition}.

\vspace{1em}

\begin{stepbox}{Step 3A: Explicit Derivation of the Exact Potential $f(x,y)$}
\textbf{Passage 1: The Intuition}\\
Imagine fluid flowing through our 2D disk. The original vector field $\vec{V}$ dictates how the fluid moves, including how it pushes in and out of the boundary edge. Because we already forced Team Co-exact ($\vec{C}$) to follow a Dirichlet condition ($\vec{C} \cdot \hat{n} = 0$), it is banned from crossing the border. Therefore, Team Exact ($\nabla f$) must handle 100\% of the boundary flux. This division of labor is what the Neumann boundary condition represents.

\textbf{Passage 2: The Algebraic Derivation}\\
We start with our fundamental decomposition on the boundary $\partial D$: $\vec{V} = \nabla f + \vec{C}$. Taking the dot product with the normal vector gives $\vec{V} \cdot \hat{n} = (\nabla f \cdot \hat{n}) + (\vec{C} \cdot \hat{n})$. Because $\vec{C} \cdot \hat{n} = 0$, the term vanishes. Since $\nabla f \cdot \hat{n}$ is the normal directional derivative $\frac{\partial f}{\partial n}$, we are left with our strict rule: $\frac{\partial f}{\partial n} = \vec{V} \cdot \hat{n}$.

\textbf{Passage 3: Finding Our Target Boundary Condition}\\
We evaluate $\vec{V} \cdot \hat{n}$ using our specific vector field $\vec{V} = \langle x^2y, xy^2 \rangle$ and unit normal $\hat{n} = \langle x, y \rangle$. The dot product yields $x^3y + xy^3 = xy(x^2 + y^2)$. Because we are strictly evaluating this on the boundary (the unit circle where $x^2 + y^2 = 1$), this simplifies perfectly to $\vec{V} \cdot \hat{n} = xy(1) = xy$. Thus, our exact potential must satisfy $\frac{\partial f}{\partial n} = xy$.

\textbf{Passage 4: Testing Our Particular Solution}\\
Our particular solution for the interior Poisson equation ($\nabla^2 f = 4xy$) is $f_p(x,y) = \frac{1}{3}(x^3y + xy^3)$. Does it meet the boundary target? The gradient is $\nabla f_p = \langle x^2y + \frac{1}{3}y^3, \frac{1}{3}x^3 + xy^2 \rangle$. Dotting this with $\hat{n} = \langle x,y \rangle$ gives $\frac{4}{3}x^3y + \frac{4}{3}xy^3 = \frac{4}{3}xy(x^2 + y^2)$. On the boundary, this becomes $\frac{4}{3}xy$. Our target is $1xy$, meaning our solution is pushing too much fluid across the border.

\textbf{Passage 5: The Harmonic Correction}\\
We must subtract exactly $\frac{1}{3}xy$ from the boundary flow. To avoid ruining the interior Poisson equation we already solved, we add a harmonic function $h(x,y)$ where $\nabla^2 h = 0$ and $\frac{\partial h}{\partial n} = -\frac{1}{3}xy$. A simple polynomial $h(x,y) = Cxy$ yields $\frac{\partial h}{\partial n} = 2Cxy$. Setting $2Cxy = -\frac{1}{3}xy$ gives $C = -\frac{1}{6}$. Therefore, our correcting harmonic function is $h(x,y) = -\frac{1}{6}xy$.

\vspace{0.5em}
\hrule
\vspace{0.5em}
\textbf{Final Solution:} 
\[ f(x,y) = f_p(x,y) + h(x,y) = \frac{1}{3}(x^3y + xy^3) - \frac{1}{6}xy \]
\end{stepbox}

\begin{stepbox}{Step 3B: Solving for the Co-Exact Potential $g(x,y)$}
\textbf{Particular Solution:} $\nabla^2 g = x^2 - y^2 \implies g_p = \frac{1}{12}(x^4 - y^4)$. \\
\textbf{Harmonic Correction:} To satisfy the Dirichlet boundary condition ($g=0$) on the unit circle, we subtract the harmonic function $h(x,y) = \frac{1}{12}(x^2 - y^2)$. 

\vspace{0.5em}
\hrule
\vspace{0.5em}
\textbf{Final Solution:} 
\[ g(x,y) = \frac{1}{12}(x^4 - y^4) - \frac{1}{12}(x^2 - y^2) \]
\end{stepbox}

\section{Explicit Computation of Energies \& Exactness}
To compute the exact energies (the $L^2$ norms squared) over the unit disk $D$, we convert the vector magnitudes to \textbf{polar coordinates} $(r, \theta)$, where $x = r\cos\theta$ and $y = r\sin\theta$. The area element becomes $dA = r \, dr \, d\theta$, and we integrate over $r \in [0, 1]$ and $\theta \in [0, 2\pi]$.

\begin{stepbox}{Step 1: The Total Energy of the Original Field ($\|\omega\|^2$)}
Our original vector field is $\vec{V} = \langle x^2y, xy^2 \rangle$. We find the squared magnitude $|\vec{V}|^2$ and convert to polar:
\begin{align*}
|\vec{V}|^2 &= (x^2y)^2 + (xy^2)^2 = x^4y^2 + x^2y^4 = x^2y^2(x^2 + y^2) \\
&= (r^2\cos^2\theta)(r^2\sin^2\theta)(r^2) = r^4\left(\frac{1}{2}\sin(2\theta)\right)^2(r^2) \\
&= \frac{1}{4}r^6\sin^2(2\theta)
\end{align*}
Now, we integrate this over the unit disk using $dA = r \, dr \, d\theta$:
\begin{align*}
\|\omega\|^2 &= \int_0^{2\pi} \int_0^1 \left( \frac{1}{4}r^6\sin^2(2\theta) \right) r \, dr \, d\theta \\
&= \frac{1}{4} \left( \int_0^{2\pi} \sin^2(2\theta) \, d\theta \right) \left( \int_0^1 r^7 \, dr \right) \\
&= \frac{1}{4} (\pi) \left[ \frac{1}{8}r^8 \right]_0^1 = \frac{1}{4} (\pi) \left( \frac{1}{8} \right) = \frac{\pi}{32}
\end{align*}
\end{stepbox}

\begin{stepbox}{Step 2: The Energy of the Exact Part ($\|df\|^2$)}
We found our exact scalar potential to be $f(x,y) = \frac{1}{3}xy(x^2+y^2) - \frac{1}{6}xy$. In polar coordinates:
\begin{align*}
f(r,\theta) &= \frac{1}{3}\left(\frac{1}{2}r^2\sin(2\theta)\right)(r^2) - \frac{1}{6}\left(\frac{1}{2}r^2\sin(2\theta)\right) \\
&= \left( \frac{1}{6}r^4 - \frac{1}{12}r^2 \right) \sin(2\theta)
\end{align*}
The exact part is the gradient field $\nabla f$. The squared magnitude is $|\nabla f|^2 = (f_r)^2 + \frac{1}{r^2}(f_\theta)^2$. Computing the derivatives and squaring them:
\begin{align*}
f_r^2 &= \left(\frac{2}{3}r^3 - \frac{1}{6}r\right)^2\sin^2(2\theta) = \left(\frac{4}{9}r^6 - \frac{2}{9}r^4 + \frac{1}{36}r^2\right)\sin^2(2\theta) \\
\frac{1}{r^2}f_\theta^2 &= \frac{1}{r^2}\left[ \left(\frac{1}{3}r^4 - \frac{1}{6}r^2\right) 2\cos(2\theta) \right]^2 = \left(\frac{1}{9}r^6 - \frac{1}{9}r^4 + \frac{1}{36}r^2\right)\cos^2(2\theta)
\end{align*}
Integrating over the disk, the angular integrals $\int_0^{2\pi}\sin^2(2\theta)d\theta$ and $\int_0^{2\pi}\cos^2(2\theta)d\theta$ both evaluate to $\pi$. We sum the radial polynomials and multiply by the area element $r$:
\begin{align*}
\|df\|^2 &= \pi \int_0^1 \left[ \left(\frac{4}{9}r^6 - \frac{2}{9}r^4 + \frac{1}{36}r^2\right) + \left(\frac{1}{9}r^6 - \frac{1}{9}r^4 + \frac{1}{36}r^2\right) \right] r \, dr \\
&= \pi \int_0^1 \left( \frac{5}{9}r^6 - \frac{1}{3}r^4 + \frac{1}{18}r^2 \right) r \, dr = \pi \int_0^1 \left( \frac{5}{9}r^7 - \frac{1}{3}r^5 + \frac{1}{18}r^3 \right) \, dr \\
&= \pi \left[ \frac{5}{72}r^8 - \frac{1}{18}r^6 + \frac{1}{72}r^4 \right]_0^1 = \pi \left( \frac{5}{72} - \frac{4}{72} + \frac{1}{72} \right) = \frac{2\pi}{72} = \frac{\pi}{36}
\end{align*}
\end{stepbox}

\begin{stepbox}{Step 3: The Energy of the Co-Exact Part ($\|\delta\beta\|^2$)}
Our co-exact scalar potential is $g(x,y) = \frac{1}{12}(x^4 - y^4) - \frac{1}{12}(x^2 - y^2)$. In polar coordinates:
\[ g(r,\theta) = \frac{1}{12}r^4\cos(2\theta) - \frac{1}{12}r^2\cos(2\theta) = \left( \frac{1}{12}r^4 - \frac{1}{12}r^2 \right) \cos(2\theta) \]
The co-exact field is $\vec{C} = \langle g_y, -g_x \rangle$. Since $g_y^2 + (-g_x)^2 = |\nabla g|^2$, we use the exact same polar gradient formula. Computing the derivatives and squaring them:
\begin{align*}
g_r^2 &= \left(\frac{1}{3}r^3 - \frac{1}{6}r\right)^2\cos^2(2\theta) = \left(\frac{1}{9}r^6 - \frac{1}{9}r^4 + \frac{1}{36}r^2\right)\cos^2(2\theta) \\
\frac{1}{r^2}g_\theta^2 &= \frac{1}{r^2}\left[ -\left(\frac{1}{6}r^4 - \frac{1}{6}r^2\right)\sin(2\theta) \right]^2 = \left(\frac{1}{36}r^6 - \frac{1}{18}r^4 + \frac{1}{36}r^2\right)\sin^2(2\theta)
\end{align*}
Again, angular integration yields $\pi$ for both terms. Summing the radial polynomials multiplied by $r$:
\begin{align*}
\|\delta\beta\|^2 &= \pi \int_0^1 \left[ \left(\frac{1}{9}r^6 - \frac{1}{9}r^4 + \frac{1}{36}r^2\right) + \left(\frac{1}{36}r^6 - \frac{1}{18}r^4 + \frac{1}{36}r^2\right) \right] r \, dr \\
&= \pi \int_0^1 \left( \frac{5}{36}r^7 - \frac{1}{6}r^5 + \frac{1}{18}r^3 \right) \, dr \\
&= \pi \left[ \frac{5}{288}r^8 - \frac{1}{36}r^6 + \frac{1}{72}r^4 \right]_0^1 = \pi \left( \frac{5}{288} - \frac{8}{288} + \frac{4}{288} \right) = \frac{\pi}{288}
\end{align*}
\end{stepbox}

\begin{stepbox}{Step 4: The Final Percentage}
First, we verify that the Hodge Decomposition worked perfectly. Orthogonality dictates that the exact and co-exact energies must sum to the total energy:
\[ \|df\|^2 + \|\delta\beta\|^2 = \frac{\pi}{36} + \frac{\pi}{288} = \frac{8\pi}{288} + \frac{\pi}{288} = \frac{9\pi}{288} = \frac{\pi}{32} \]
This matches our total energy $\|\omega\|^2$ exactly!

Finally, the percentage of exactness is the ratio of the exact energy to the total energy:
\[ \text{Percentage Exact} = \frac{\|df\|^2}{\|\omega\|^2} = \frac{\pi/36}{\pi/32} = \frac{32}{36} = \frac{8}{9} \approx 88.89\% \]

\vspace{0.5em}
\hrule
\vspace{0.5em}
\textbf{Conclusion:} Even though $\omega = x^2y \, dx + xy^2 \, dy$ is officially non-exact, we have quantitatively proven that over a unit disk, \textbf{88.89\%} of its energy behaves perfectly conservatively. Only the remaining 11.11\% contributes to the non-exact, path-dependent swirl.
\end{stepbox}

\end{document}
